Inefficient Concessions and Mediation

### 2021-01-02 notes.tex
add constraints for g1 case

\color{blue} I think it's possible that this condition can never be satisfied (i.e. if e=1 is IC, you'd never want to call in the mediator). But I haven't tried to prove it yet

>>>>

I've used Mathematica to find a parameterization under which this is true.
\begin{itemize}
	\item I implemented the constraint in Mathematica to make sure the gift under $e=1$ is positive, BUT I did not implement the constraint on $\de_h$ that makes it IC (although I have a check in ``e-g calculations.R''. Here is the constraint on $\de_h$:
		\[
		  \de_h \geq D + 1 - p(T+D) + \frac{p(W-(T+D))}{g^1}
		\]
\end{itemize}
